Testing gene methylation enrichment analysis approaches using simulated data

### 2023-11-02 figs/GSE158422_simulate020.Rmd
simulation results good
updates on data presentation

gres2 <- do.call(rbind,lapply(gres,colMeans))

@@

lacres2 <- do.call(rbind,lapply(lacres,colMeans))

@@

lactopres2 <- do.call(rbind,lapply(lactopres,colMeans))

@@

nlacres2 <- do.call(rbind,lapply(nlacres,colMeans))

@@

lacmres2 <- do.call(rbind,lapply(lacmres,colMeans))

@@

alcres2 <- do.call(rbind,lapply(alcres,colMeans))

@@

nalcres2 <- do.call(rbind,lapply(nalcres,colMeans))

@@

almres2 <- do.call(rbind,lapply(almres,colMeans))

@@

aares

aares2 <- do.call(rbind,lapply(aares,colMeans))

aares2

@@

save.image("GSE158422_simulate.Rdata")

>>>>

gres2 <- do.call(rbind,lapply(gres,colMeans))
gres2[,"PREC"] <- gres2[,"TP"] / ( gres2[,"TP"] + gres2[,"FP"] )

@@

lacres2 <- do.call(rbind,lapply(lacres,colMeans))
lacres2[,"PREC"] <- lacres2[,"TP"] / ( lacres2[,"TP"] + lacres2[,"FP"] )

@@

lactopres2 <- do.call(rbind,lapply(lactopres,colMeans))
lactopres2[,"PREC"] <- lactopres2[,"TP"] / ( lactopres2[,"TP"] + lactopres2[,"FP"] )

@@

nlacres2 <- do.call(rbind,lapply(nlacres,colMeans))
nlacres2[,"PREC"] <- nlacres2[,"TP"] / ( nlacres2[,"TP"] + nlacres2[,"FP"] )

@@

lacmres2 <- do.call(rbind,lapply(lacmres,colMeans))
lacmres2[,"PREC"] <- lacmres2[,"TP"] / ( lacmres2[,"TP"] + lacmres2[,"FP"] )

@@

alcres2 <- do.call(rbind,lapply(alcres,colMeans))
alcres2[,"PREC"] <- alcres2[,"TP"] / ( alcres2[,"TP"] + alcres2[,"FP"] )

@@

nalcres2 <- do.call(rbind,lapply(nalcres,colMeans))
nalcres2[,"PREC"] <- nalcres2[,"TP"] / ( nalcres2[,"TP"] + nalcres2[,"FP"] )

@@

almres2 <- do.call(rbind,lapply(almres,colMeans))
almres2[,"PREC"] <- almres2[,"TP"] / ( almres2[,"TP"] + almres2[,"FP"] )

@@

aares2 <- do.call(rbind,lapply(aares,colMeans))
aares2[,"PREC"] <- aares2[,"TP"] / ( aares2[,"TP"] + aares2[,"FP"] )

@@

save.image("GSE158422_simulate020.Rdata")
